---
title: "Sentiment Analysis of Tweets about Bernie"
subtitle: ""
output:
  github_document
allow_html: true
editor_options:
  chunk_output_type: console
---
  
## Setup

```{r libs}

library(tidyverse)
library(here)
library(rtweet)
library(tidytext)

```

```{r theme_chunk_opts}

theme_set(theme_light())

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      fig.width = 10,
                      fig.height = 7)

```

### Sentiments behind tweets containing "Bernie"/"Sanders" and "socialist"/"socialism"

I'm curious about the sentiments in tweets that mention Bernie and socialist/socialism-- are more people deriding his socialist tendencies or supporting them?

```{r bernie_socialist_info}

bernie_socialist_info <- search_tweets(q = "bernie socialist",
                                       n = 10000,
                                       include_rts = FALSE, 
                                       #type = "popular",
                                       retryonratelimit = TRUE)


```

```{r}

bernie_socialist_info %>% 
  select(user_id, status_id, screen_name, text) %>% 
  unnest_tokens(output = word, input = text) %>% 
  filter(!word %in% stop_words$word) %>% 
  View()
  
```

### Sentiments from specific users

Next, I'll look at tweets from people who I consider to be Leftists, Centrists, and Right-Wingers and figure out the sentiments in their tweets about Bernie.

**Leftist**

- Jordan Uhl ()
- Ken Klippenstein ()
- Jacobin Mag ()

**Centrist**

- Jennifer Rubin (@JRubinBlogger)
- Jake Tapper ()
- CNN

**Right-Wing**

- Charlie Kirk ()
- Dan Bongino ()
- Ben Shapiro ()


```{r}



```







